\begin{abstract}

In a test suite, all the test cases should be independent:
no test should affect any other test's result, and running
the tests in any order should produce the same test results.
The assumption of test independence is important so that
tests behave consistently as designed. In addition, many
downstream testing techniques, including test prioritization,
test selection, and test parallelization,
assume test independence.
Our recent work shows this critical
assumption often does not hold in practice. However, the impact
of test dependence is still unclear. In this paper, we
empircally investigate the impact of test dependence
and propose techniques to cope with its impact.
We present three results.

First, we describe an empirical study to assess the impact of test dependence
on \prionum test prioritization, \selnum test selection, and
\parnum test parallelization
algorithms. The study suggests that test dependence
affects the results of \textit{all} evaluated downstream
testing algorithms.

Second, we present a family of techniques to cope with the impact
of test dependence by enhancing existing
test prioritization, selection, and parallelization
techniques to ensure they respect the test dependence . 
%The first technique monitors the
%test execution of a test suite and generates a concise report
%to describe the root cause of test dependence.
%The report permits developers understand why and how
%test dependence arises.
%The second technique enhances existing test prioritization,
%test selection, and test parallelization algorithms to ensure
%they respect the test dependence.

Third, we describe an experimental evaluation 
to show that all enhanced testing techniques
output consistent results in the presence of
test dependence without compromising their effectiveness.

%techniques for coping with
%the test dependence impact are useful and effective. They
%help developers understand why and how test dependence arises
%and enable downstream techniques output consistent results
%in the presence of test dependence.

\end{abstract}

