

\begin{itemize}

\item \todo{KM}{I kind of understand what this paragraph is saying.
However the many minor mistakes in the writing make it very hard to
follow up.} Patterns of dependent tests.
In many cases, there is a \textit{N -- 1} \todo{KM}{The first time I read this,
I read as N minus 1, which is the incorrect way. Maybe write down as ``N to 1''}
dependence relationship, in which $N$-th \todo{KM}{Is ``th'' really needed?} distinct tests depends\todo{KM}{This should be either ``tests depend on'' (more likely) or ``test depends on'', but I couldn't decide} on the same test, which probably is used to set up the environment. For
such cases, the 1 depend test \todo{KM}{``1 dependent test'' or ``first
dependent test''} should be moved to the common \CodeIn{setUp}
\todo{KM}{Consistency: consider @Before} method.
Less frequently, there is a \textit{1 -- N} dependence relationship
\todo{KM}{Have we ever seen this, or is this purely theoretical?}, in which one
test depends on $N$ tests to set up its testing environment.  In one subject, a newly-added test changes the shared variable state of an existing test. Although the newly-added test is executed after the existing test and reveals the same behavior when executing in isolation, the existing test exhibit different behavior if it is executed after the newly-added test.


\item 
\todo{JW}{If we really want to discuss this, this should be connected
to the theory section, as all this follows from theory. A ``finding''
might be that these differences actually matter in practice. And I
don't think we checked that.}
Different techniques have their own strength in detecting dependent tests. We
have investigate three methods (i.e., executing in isolation, executing in a
reversed order\todo{KM}{Did we (do we) really do this?}, and executing in
k-permutation) to identify dependent tests, and found each method complements others. There exist certain tests that can only be found by one method
but missed by the other two.  Executing tests in isolation found more dependent tests
than executing in a reversed order, and executing every $k$-permutation is
infeasible in practice due to the exponentially large number of possible combinations.

\end{itemize}
